---
title: "aescos_omics_PEC1"
output: html_document
date: "2024-11-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To erase data and start clean:

```{r, message=FALSE, warning=FALSE}
rm(list = ls())
```

To push changes in Git after working on the PEC1.

```{bash eval=FALSE, include=FALSE}
git push -u origin main
# They will ask about the user name in github (aescos)
# and password (use PAT token for this month)
```

Los datos que voy a emplear: Descripcion:

"The acompanying dataset has been obtained from a phosphoproteomics experiment that was performed to analyze (3 + 3) PDX models of two different subtypes using Phosphopeptide enriched samples. LC-MS analysis of 2 technical duplicates has been performed on each sample. The results set consisted of Normalized abundances of MS signals for ca. 1400 phosphopeptides Goal of the analysis: *search phosphopeptides that allow differentiation of the two tumor groups This should be made with both Statistical Analysis and visualization. Data have been provided as an excel file: TIO2+PTYR-human-MSS+MSIvsPD.XLSX

Groups are defined as:

MSS group: Samples M1, M5 and T49,
PD group: Samples M42, M43 and M64 with two technical replicates for each sample The first column, SequenceModification contains abundance values for the distinct phosphopetides. Other columns can be omitted."

```{r}
library(readxl)
data_phospho <- read_excel("TIO2+PTYR-human-MSS+MSIvsPD.XLSX")
View(data_phospho)

targets <- read_excel("TIO2+PTYR-human-MSS+MSIvsPD.XLSX", sheet = "targets")
View(targets)
```

